A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-01-26 pilot-publication/manuscript.Rmd
Add TQIP cohort to sample characteristics table

Within each combination of trial arms we conducted subgroup analyses of men, women, blunt multisystem trauma, penetrating trauma, shock, severe traumatic brain injury, and elderly. Table S7.1 in Supplemental Material 7 shows which outcomes that were assessed in what subgroups, decided through consensus in the research team. We further compared the results of all subgroups with the results in the whole cohort, and compared the results in the female subgroup with the male subgroup, and the results in the blunt multisystem trauma subgroup with the penetrating trauma subgroup. We are aware that the numbers in some of these subgroups are small, but we included them to help guide the formulation of the statistical analysis plan for the full-scale trial.

@@

The absolute risk difference between the standard care and ATLS arms (95% CI) was `r arr.standard.care.atls`% units, between the standard care and PTC arms (95% CI) `r arr.standard.care.ptc`% units, and between the ATLS and PTC arms (95% CI) `r arr.atls.ptc`% units. The relative risk in the standard care arm compared with the ATLS arm (95% CI) was `r rr.standard.care.atls`, in the standard care arm compared with the PTC arm (95% CI) `r rr.standard.care.ptc`, and in the ATLS arm compared with the PTC arm (95% CI) the relative risk was `r rr.atls.ptc`. The absolute and relative differences in changes from baseline comparing the three arms are shown in Supplementary materials, along with data on all other outcomes.

>>>>

Within each combination of trial arms we had planned to conduct subgroup analyses of men, women, blunt multisystem trauma, penetrating trauma, shock, severe traumatic brain injury, and elderly. These subgroups were however too small to allow for meaningful analyses, and are therefore reported descriptively only.

@@

The absolute risk difference between the standard care and ATLS arms (95% CI) was `r arr.standard.care.atls`% units, between the standard care and PTC arms (95% CI) `r arr.standard.care.ptc`% units, and between the ATLS and PTC arms (95% CI) `r arr.atls.ptc`% units. The relative risk in the standard care arm compared with the ATLS arm (95% CI) was `r rr.standard.care.atls`, in the standard care arm compared with the PTC arm (95% CI) `r rr.standard.care.ptc`, and in the ATLS arm compared with the PTC arm (95% CI) the relative risk was `r rr.atls.ptc`. The absolute and relative differences in changes from baseline comparing the three arms are shown in Supplementary materials, along with data on all secondary outcomes.
